### 2023-03-13 main/chapter_2ljets.tex
add int trigger table

In total, we use $14$ different two-lepton trigger selections, each of which
selects for an electron pair, a muon pair, or an emu (electron-muon pair).
To describe those triggers, we use $\pt^{\ell_i}$ for the transverse momentum
of the $i\mathrm{th}$ hardest lepton.
All triggers require $\pt^{\ell_i}$ values to exceed thresholds in
the range $8\textrm{--}26\,\eV[G]$.
To detail all trigger requirements and their variations with data period
would be too tedious and not enlightening, but their $\pt^{\ell_i}$ requirements
are summarized here.
Please do not read them all in detail ---
the point of this listing is to show trigger activations are varied and
non-trivial.
\begin{itemize}
\item Electron pair: requirements vary between $\pt^{e_2} > 12\,\eV[G]$ and
$\pt^{e_2} > 17\,\eV[G]$.
\item Muon pair: various requirements include
$\pt^{\mu_2} > 10\,\eV[G]$,
$\pt^{\mu_2} > 14\,\eV[G]$,
$\pt^{\mu_1} > 18\,\eV[G]~\&~\pt^{\mu_2} > 8\,\eV[G]$, and
$\pt^{\mu_1} > 22\,\eV[G]~\&~\pt^{\mu_2} > 8\,\eV[G]$.
\item Emu pair: various asymmetric requirements include
$\pt^{e_1} > 17\,\eV[G]~\&~\pt^{\mu_1} > 14\,\eV[G]$,
$\pt^{e_1} > 7\,\eV[G]~\&~\pt^{\mu_1} > 24\,\eV[G]$, and
$\pt^{e_1} > 26\,\eV[G]~\&~\pt^{\mu_1} > 8\,\eV[G]$.
\end{itemize}
Trigger requirements have increased in hardness with time throughout the data
used in $\twoljets$.

@@

>>>>

In total, we use $14$ different two-lepton trigger selections, each of which
selects for an electron pair, a muon pair, or an emu (electron-muon pair).
To describe those triggers, we use $\pt^{\ell_i}$ for the transverse momentum
of the $i\mathrm{th}$ hardest lepton.
All triggers require $\pt^{\ell_i}$ values to exceed thresholds in
the range $8\textrm{--}26\,\eV[G]$.
To detail all trigger requirements and their variations with data period
would be too tedious and not enlightening, but their $\pt^{\ell_i}$ requirements
are summarized here.
Please do not read them all in detail ---
the point of this listing is to show trigger activations are varied and
non-trivial.
\begin{itemize}
\item Electron pair: requirements vary between $\pt^{e_2} > 12\,\eV[G]$ and
$\pt^{e_2} > 17\,\eV[G]$.
\item Muon pair: various requirements include
$\pt^{\mu_2} > 10\,\eV[G]$,
$\pt^{\mu_2} > 14\,\eV[G]$,
$\pt^{\mu_1} > 18\,\eV[G]~\&~\pt^{\mu_2} > 8\,\eV[G]$, and
$\pt^{\mu_1} > 22\,\eV[G]~\&~\pt^{\mu_2} > 8\,\eV[G]$.
\item Emu pair: various asymmetric requirements include
$\pt^{e_1} > 17\,\eV[G]~\&~\pt^{\mu_1} > 14\,\eV[G]$,
$\pt^{e_1} > 7\,\eV[G]~\&~\pt^{\mu_1} > 24\,\eV[G]$, and
$\pt^{e_1} > 26\,\eV[G]~\&~\pt^{\mu_1} > 8\,\eV[G]$.
\end{itemize}
Trigger requirements have increased in hardness with time throughout the data
used in $\twoljets$.
A more detailed listing of our trigger choices is presented in
Table~\ref{tab:2ljets_trigger_int}.

@@

\begin{table}[tp]
\centering
\begin{tabular}{ccll}
Year & $\ell\ell$ & Trigger & Comment
\\[0.2em]
\hline
2015 & $ee$     & {\footnotesize HLT\_2e12\_lhloose\_L12EM10VH} & \\
2015 & $\mu\mu$ & {\footnotesize HLT\_2mu10} & \\
2015 & $\mu\mu$ & {\footnotesize HLT\_mu18\_mu8noL1} & \\
2015 & $e\mu$   & {\footnotesize HLT\_e17\_lhloose\_mu14} & \\
2015 & $e\mu$   & {\footnotesize HLT\_e7\_lhmedium\_mu24} & \\[0.8em]
%
2016 & $ee$     & {\footnotesize HLT\_2e15\_lhvloose\_nod0\_L12EM13VH} & except run 300540 \\
2016 & $ee$     & {\footnotesize HLT\_2e17\_lhvloose\_nod0} & run 300540, periods D4-- \\
2016 & $\mu\mu$ & {\footnotesize HLT\_2mu10} & period A \\
2016 & $\mu\mu$ & {\footnotesize HLT\_2mu14} & from period B \\
2016 & $\mu\mu$ & {\footnotesize HLT\_mu20\_mu8noL1} & periods A-D3 \\
2016 & $\mu\mu$ & {\footnotesize HLT\_mu22\_mu8noL1} & periods from D4 \\
2016 & $e\mu$   & {\footnotesize HLT\_e17\_lhloose\_nod0\_mu14} & \\
2016 & $e\mu$   & {\footnotesize HLT\_e24\_lhmedium\_nod0\_L1EM20VHI\_mu8noL1}\hspace{-3em} & \\
2016 & $e\mu$   & {\footnotesize HLT\_e7\_lhmedium\_nod0\_mu24} & \\[0.8em]
%
2017 & $ee$     & {\footnotesize HLT\_2e17\_lhvloose\_nod0\_L12EM15VHI} & except periods B5--B8 \\
2017 & $ee$     & {\footnotesize HLT\_2e24\_lhvloose\_nod0} & \\
2017 & $\mu\mu$ & {\footnotesize HLT\_2mu14} & \\
2017 & $\mu\mu$ & {\footnotesize HLT\_mu22\_mu8noL1} & \\
2017 & $e\mu$   & {\footnotesize HLT\_e17\_lhloose\_nod0\_mu14} & \\
2017 & $e\mu$   & {\footnotesize HLT\_e26\_lhmedium\_nod0\_mu8noL1} & \\
2017 & $e\mu$   & {\footnotesize HLT\_e7\_lhmedium\_nod0\_mu24} & \\[0.8em]
%
2018 & $ee$     & {\footnotesize HLT\_2e17\_lhvloose\_nod0\_L12EM15VHI} & \\
2018 & $ee$     & {\footnotesize HLT\_2e24\_lhvloose\_nod0} & \\
2018 & $\mu\mu$ & {\footnotesize HLT\_2mu14} & \\
2018 & $\mu\mu$ & {\footnotesize HLT\_mu22\_mu8noL1} & \\
2018 & $e\mu$   & {\footnotesize HLT\_e17\_lhloose\_nod0\_mu14} & \\
2018 & $e\mu$   & {\footnotesize HLT\_e26\_lhmedium\_nod0\_mu8noL1} & \\
2018 & $e\mu$   & {\footnotesize HLT\_e7\_lhmedium\_nod0\_mu24} & \\
\end{tabular}
\caption[
Detailed trigger specifications
]{
Detailed trigger specifications for the $\twoljets$ analysis in all four
years of Run~2.
These are the dilepton triggers with the weakest available requirements.
Some information can be scraped from the name of each trigger.
Run numbers and periods mentioned in the ``Comment'' column indicate specific
parts of each LHC run, and are chosen on the advice of internal \atlas\
documentation and relate to local operating
conditions~\cite{atlas_twiki_lowest_unprescaled}.
This table is adapted from supporting material for the $\twoljets$ search
paper~\cite{atlas2022searches}.
}
\label{tab:2ljets_trigger_int}
\end{table}
